Cross Validation Analysis

### 2023-03-08 minos/validation/cross_validation.Rmd
Created functions for processing data (combining multiple sources, pivoting, and summarising), producing plots to compare means, and producing box plots. Also have some code for running t-tests

cv <- cv %>% filter(pidp %in% both.pidps$pidp)
raw <- raw %>% filter(pidp %in% both.pidps$pidp)

#cv2 <- cv[cv$pidp %in% both.pidps]
```

@@

```{r}
income.cv <- cv %>% 
  select(pidp, time, hh_income)

income.raw <- raw %>%
  select(pidp, time, hh_income)

# first rename and cbind
income.cv <- rename(income.cv, simulation = hh_income)
income.raw <- rename(income.raw, raw = hh_income)

income.merged <- merge(income.cv, income.raw, by=c('pidp', 'time'))

income.merged <- pivot_longer(data = income.merged,
                              cols = simulation:raw,
                              names_to = 'scenario',
                              values_to = 'hh_income')

income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))

@@

>>>>

cv <- cv %>% filter(pidp %in% both.pidps$pidp)
raw <- raw %>% filter(pidp %in% both.pidps$pidp)
```

@@

```{r}
income.pivoted <- combine_and_pivot_long(cv, 'simulated', raw, 'raw', 'hh_income')

income.merged.byyr <- income.pivoted %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))

@@

```{r}
qqnorm(cv$hh_income)
qqnorm(raw$hh_income)

# Check variance of both
cv.inc.var <- var(cv$hh_income)
raw.inc.var <- var(raw$hh_income, na.rm = TRUE)

# if ratio of largest variance to smallest is less than 4 then assume variance is equal for t.test
(raw.inc.var / cv.inc.var) < 4

test.t <- t.test(cv$hh_income, raw$hh_income, var.equal = TRUE)

for(year in unique(cv$time)) {
  print(paste('T tests for year', year))
  # filter the year
  tmp.cv <- cv %>% filter(time == year)
  tmp.raw <- raw %>% filter(time == year)

  # check variance and test for equal variance
  var.tmp.cv <- var(tmp.cv$hh_income)
  var.tmp.raw <- var(tmp.raw$hh_income, na.rm = TRUE)

  if(var.tmp.raw > var.tmp.cv) {
    equal.var <- (var.tmp.cv / var.tmp.raw) < 4
  } else {
    equal.var <- (var.tmp.raw / var.tmp.cv) < 4
  }

  print(t.test(tmp.cv$hh_income, tmp.raw$hh_income, var.equal = equal.var))
}
```

```{r}
compare_boxplot_long(income.pivoted,
                    var = 'hh_income',
                    scen1 = 'raw',
                    scen2 = 'simulation',
                    subset.max = 5000,
                    subset.min = -5000)
```
